---
title: "Format COVID Resources "
output: html_notebook
---

```{r}
library(tidyverse)
```



# Purpose

The purpose of this notebook to format the data received from the Community Alignment Specialist for use with the COVID Agency finder shiny app. 


## Import Data

Import the data exactly as it was from the google sheet.

```{r}
resources <- read_csv("resources.csv")
```


## Data cleaning

Rename columns so there are no hypens or spaces! You will thank me later!

```{r}
resources2 <- rename(resources,
                     Program = 'Program Name',
                     lastUpdated = 'Last Updated',
                     Mon = 'Mon-Hours',
                     Tue = 'Tues-Hours',
                     Wed = 'Wed-Hours',
                     Thu = 'Thur-Hours',
                     Fri = 'Fri-Hours',
                     Sat = 'Sat-Hours',
                     Sun = 'Sun-Hours',
                     Address1 = 'Street Address',
                     Address2 = 'Addressline 2',
                     Description = 'Program Description')
```




Always need to clean your data. Check to see if there are blank rows that might have been used to improve readibility but serve no function in a database.

```{r}
#drop rows in df resources where column 'Organization' is NA
resources2 <-drop_na(resources2, Organization)
```


Program column can not be left blank. If there is a NA in that column replace NA with the value for the Organization Column.

```{r}

resources2$Program <- if_else(is.na(resources2$Program), #test condition 
                              resources2$Organization,   #value if test TRUE
                              resources2$Program)       #value if test FALSE  


```



Replace NA's from operating hours. If column is NA, then replace it with 'Closed'.


```{r}
resources3 <- replace_na(resources2,
                         list(Mon = "Closed", Tue ="Closed")
) 
```













