---
title: "Format COVID Resources "
output: html_notebook
---


```{r message=FALSE}
library(tidyverse)
library(config)
library(ggmap)
library(googlesheets4)
library(httr)
```


IMPORTANT!!!! Must run gs4_auth() in console to get credentials to work!


# Purpose

The purpose of this notebook to format the data received from the Community Alignment Specialist for use with the COVID Agency finder shiny app. 


## Import Data

Import the data exactly as it was from the google sheet.

```{r}
gs_inputData <- read_sheet("https://docs.google.com/spreadsheets/d/1bSd_SqkWOQMdgAkzsCbOLFK6nQy5OiYVWzzNi4ZuEoo/edit?usp=sharing")
```

## Data cleaning

Rename columns so there are no hypens or spaces! You will thank me later!

```{r}
gs_inputData <- rename(gs_inputData,
                     Organization = '...1',
                     Program = 'Program Name',
                     lastUpdated = 'Last Updated',
                     Mon = 'Mon-Hours',
                     Tue = 'Tues-Hours',
                     Wed = 'Wed-Hours',
                     Thu = 'Thur-Hours',
                     Fri = 'Fri-Hours',
                     Sat = 'Sat-Hours',
                     Sun = 'Sun-Hours',
                     Address1 = 'Street Address',
                     Address2 = 'Addressline 2',
                     Description = 'Program Description')
```










```{r}
unique(gs_inputData$City)
```




Fix the issue around unrecognized text
This line was deleted by Katelyn 

```{r}
                     

gs_inputData$City[gs_inputData$Program=="Grab & Go Meals - Laurelwood Apartments"] <- "High Point"

unique(gs_inputData$City)
```



```{r}
gs_inputData <- mutate_at(gs_inputData, 
                        "City",
                        str_replace_all,
                        pattern = "HIgh Point",
                        replacement = "High Point"
                                   
                        
)

unique(gs_inputData$City)
```







Check to see if there are blank rows that might have been used to improve readibility but serve no function in a database.

```{r}
#drop rows in df resources where column 'Organization' is NA
gs_inputData <-drop_na(gs_inputData, Organization)
```


Program column can not be left blank. If there is a NA in that column replace NA with the value for the Organization Column.

```{r}

gs_inputData$Program <- if_else(is.na(gs_inputData$Program), #test condition 
                              gs_inputData$Organization,   #value if test TRUE
                              gs_inputData$Program)       #value if test FALSE  


```



Replace blank cells in spreadsheet with the following text.


```{r warning=TRUE}
gs_inputData<- replace_na(gs_inputData,
                         list(Mon = "",
                              Tue = "",
                              Wed = "",
                              Thu = "",
                              Fri = "",
                              Sat = "",
                              Sun = "",
                              County = "Guilford",
                              Address1= "Guilford County",
                              City = ""
                              )
)


 
```


Trim city column so there are no blankspaces to either side. 
```{r warning=TRUE}

  
gs_inputData$City <- str_trim(gs_inputData$City, side = "both")
```










```{r}
unique(gs_inputData$City)
```





## Geocode Addresses

Create single address line to pass to Google API

```{r}
gs_inputData <-mutate(gs_inputData,
                   AddressLine = str_c(Address1, " ", City,", ", "NC" , sep = "" ))
```



Filter out any rows where the address line is NA since this will cause an error on the geocode.
```{r}
gs_inputData <- gs_inputData %>%
  filter( !is.na(AddressLine) )
  
```




Set API keys for google Geocode

```{r}
config <- config::get()

register_google(key =config$googKey )
```




```{r message=TRUE, warning=TRUE}
df_4Geocode<- gs_inputData


# Loop through the addresses to get the latitude and longitude of each address and add it to the
# df_4Geocode data frame in new columns lat and lon
for(i in 1:nrow(df_4Geocode))
{
  # Print("Working...")
  result <- geocode(df_4Geocode$AddressLine[i], output = "all", source = "google", )
  df_4Geocode$Lon[i] <- as.numeric(result$results[[1]]$geometry$location$lng)
  
  df_4Geocode$Lat[i] <- as.numeric(result$results[[1]]$geometry$location$lat)
  
  df_4Geocode$Geoaddress[i] <- as.character(result$results[[1]]$formatted_address)
}
```


Load Data into Data.World

```{r}
ssid<- "1gvbJPuxXSUwrTjyVtKJEffItIx_H73wlhxsWc0nZFtU"

sheetName <- "upload2DW"
```


```{r}
sheet_write(df_4Geocode, ssid, sheet = sheetName)
```

